---
title: "Diallel Research Report"
author: "Jinliang Yang"
date: "October 13th, 2014"
output: rmarkdown::tufte_handout

---
\begin{abstract}
This manual shows features of graphics in the \textbf{knitr} package
in detail, including the
graphical devices, plot recording, plot rearrangement, control of
plot sizes, the tikz device, figure captions, animations and other
types of plots such as \textbf{rgl} or GGobi plots.
  
\end{abstract}

The path and R package dependencies in this project were managed by `Packrat`[^r1] and `knitr`.
```{r setup}
library(knitr)
opts_knit$set(root.dir=normalizePath('../'))
```

# Phenotypic data

## Reformat Sofiane's phenotypic data to a matrix.

## data from external folder were loaded
```{r, eval=F}
source("munge/1.raw_pheno/1.A.1_format_pheno.R")
```

## plot the phentoypic data _per se_

```{r, fig.lp="cor-plot1", fig.width = 10, fig.height = 3, fig.fullwidth = TRUE, fig.cap = "phenotypic data distribution"}
source("profiling/1.pheno/1.A.1_pheno_plot.R")
```

Based on the normality test, the above seven traits show P-values range from c(). Therefore, we have no evidence to reject the normal distribution of the phenotype. 

## Levels of heterosis of the seven traits
```{r,  fig.width = 10, fig.height = 5, fig.fullwidth = TRUE, fig.cap = "Variations of the levels of heterosis"}
source("profiling/1.pheno/1.A.2_pheno_loh_plot.R")

```

## Correlation of the seven phenotypic traits
```{r, fig.width = 4, fig.height = 4, fig.cap = "Correlation plot of the seven traits"}
source("profiling/1.pheno/1.A.3_pheno_cor_plot.R")
### get the pheno per se
myp1 <- get_pheno(trait=trait, pheno="valHyb")
pairs(myp1[, 2:8], text.panel = diag, upper.panel=panel.smooth, 
      lower.panel=panel.cor, gap=0, main="", pch=19, col="grey", lwd=2)
```

some words here.

```{r, fig.width = 4, fig.height = 4, fig.cap = "Correlation plot of the seven traits"}
source("profiling/1.pheno/1.A.3_pheno_cor_plot.R")
### get percentage of BPHmax
myp2 <- get_pheno(trait=trait, pheno="pBPHmax")
pairs(myp2[, 2:8], text.panel = diag, upper.panel=panel.smooth, 
      lower.panel=panel.cor, gap=0, main="", pch=19, col="grey", lwd=2)

```

some words here.

```{r, fig.width = 4, fig.height = 4, fig.cap = "Correlation plot of the seven traits", fig.cap="pMPH"}
source("profiling/1.pheno/1.A.3_pheno_cor_plot.R")
### get percentage of BPHmax
myp3 <- get_pheno(trait=trait, pheno="pMPH")
pairs(myp3[, 2:8], text.panel = diag, upper.panel=panel.smooth, 
      lower.panel=panel.cor, gap=0, main="", pch=19, col="grey", lwd=2)

```





The Tufte-\LaTeX\ [^tufte_latex] document classes define a style similar to the style Edward Tufte uses in his books and handouts. Tufte’s style is known for its extensive use of sidenotes, tight integration of graphics with text, and well-set typography. 

# Headings

This style provides a- and b-heads (that is, `#` and `##`), demonstrated above.
An error is emitted if you try to use `###` and smaller headings.

\newthought{In his later books}[^books_be], Tufte starts each section with a bit of vertical space, a non-indented paragraph, and sets the first few words of the sentence in small caps. To accomplish this using this style, use the `\newthought` command as demonstrated at the beginning of this paragraph.

# Figures

## Margin Figures

Images and graphics play an integral role in Tufte's work. To place figures or tables in the margin you can use the `fig.margin` knitr chunk option. For example:


Note the use of the `fig.cap` chunk option to provide a figure caption. You can adjust the proportions of figures using the `fig.width` and `fig.height` chunk options. These are specified in inches, and will be automatically scaled down to fit within the handout margin.

## Equations

You can also include \LaTeX\ equations in the margin by explicitly invoking the `marginfigure` environment.

\begin{marginfigure}
$$\frac{d}{dx}\left( \int_{0}^{x} f(u)\,du\right)=f(x).$$
\caption{An equation}
\end{marginfigure}

Note the use of the `\caption` command to add additional text below the equation.

## Full Width Figures

You can arrange for figures to span across the entire page by using the `fig.fullwidth` chunk option. 


Note the use of the `fig.width` and `fig.height` chunk options to establish the proportions of the figure. Full width figures look much better if their height is minimized.

## Main Column Figures

Besides margin and full width figures, you can of course also include figures constrained to the main column.


# Sidenotes

One of the most prominent and distinctive features of this style is the extensive use of sidenotes. There is a wide margin to provide ample room for sidenotes and small figures. Any use of a footnote will automatically be converted to a sidenote. ^[This is a sidenote that was entered using a footnote.] 

If you'd like to place ancillary information in the margin without the sidenote mark (the superscript number), you can use the `\marginnote` command. \marginnote{This is a margin note.  Notice that there isn't a number preceding the note.}

Note also that the two footnote references (`tufte_latex` and `books_be`, both defined below) were also included in the margin on the first page of this document.

# Tables

You can use the **xtable** package to format \LaTeX\ tables that integrate well with the rest of the Tufte handout style. Note that it's important to set the `xtable.comment` and `xtable.booktabs` options as shown below to ensure the table is formatted correctly for inclusion in the document.

```{r, results='asis'}
library(xtable)
options(xtable.comment = FALSE)
options(xtable.booktabs = TRUE)
xtable(head(mtcars[,1:6]), caption = "First rows of mtcars")
```


[^tufte_latex]: https://code.google.com/p/tufte-latex/
[^books_be]: http://www.edwardtufte.com/tufte/books_be

[^r1]: http://rstudio.github.io/packrat/








