---
title: "Using Rmarkdown and Github for reproducible and collabrative research"
author: "Jinliang Yang"
date: "November 5, 2014"
output: beamer_presentation
---

## Setup your project

- using __github__ do the version control
- using **packrat** do the R package dependency management
- using **ProjectTemplate** to layout the directories  

```{r, eval=FALSE}
#install.packages('ProjectTemplate')
library('ProjectTemplate')
create.project('temp')
system("mv temp/* .")
system("rm -r temp/")
```
Or simply just copy your directory system everything here!

## Setup your project
\graphicspath{{../graphs/}}
\begin{figure}
\includegraphics{dir.png}
\caption{Minor allele frequency and missing rate of the about 14 million SNP on founder lines}
\label{fig:mfig1}
\end{figure}

## R Markdown
This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

